Forecasting the 2024 US General Election

### 2024-11-04 paper/paper.qmd
Update cross reference

The primary candidates in this election, Democratic vice president Kamala Harris and former Republican president Donald Trump, are expected to engage in a tight race, with polling indicating that the results could be very close. Swing states—those that do not consistently vote for one party—are vital in determining the overall outcome, as their electoral votes can sway the final result. This year's swing states are: Nevada, Michigan, Georgia, Wisconsin, Pennsylvania, and North Carolina. They expected to be battlegrounds in this election, making their polling data essential for accurate forecasts.

@@

@@

## Data Cleaning

# Model
## Model Justification
The unique structure of the electoral college voting system in the United States makes it unlikely for any candidate other than Donald Trump or Kamala Harris to be competitive in the 2024 presidential election. Given Trump's historical performance in previous campaigns, particularly the 2016 election, it is more insightful to model his election outcomes. To achieve this, we have decided to create a Bayesian Hierarchical Model.

@@

# Results

@@

# Discussion

@@

# Appendix 1

@@

# Appendix 2 : Idealized Survey

@@

# Appendix 3 : Model Details

@@

# References

>>>>

The primary candidates in this election, Democratic Vice President Kamala Harris and former Republican president Donald Trump, are expected to engage in a tight race, with polling indicating that the results could be very close. Swing states—those that do not consistently vote for one party—are vital in determining the overall outcome, as their electoral votes can sway the final result. This year's swing states are: Nevada, Michigan, Georgia, Wisconsin, Pennsylvania, and North Carolina. They expected to be battlegrounds in this election, making their polling data essential for accurate forecasts.

@@

The remainder of this paper is structured as follows: @sec-data-overview discusses the data sources and variables used in the analysis; #sec-Dataset-Features presents the visualization of results; @sec-data-cleaning explains the process of cleaning the data; @sec-model justifies the model setup, as well as assumptions and limitations; @sec-result presents the result of the models; @sec-discussion provides a discussion of the paper; @sec-appendix-one analyzed the methodology of The New York Times/Siena College pollster; @sec-appendix-two created an ideal survey of the poll. @sec-appendix-three provides a more detailed explanation of the models. Finally, @sec-reference provides a list of references.

@@

## Data Cleaning {#sec-data-cleaning}

# Model {#sec-model}
## Model Justification
The unique structure of the electoral college voting system in the United States makes it unlikely for any candidate other than Donald Trump or Kamala Harris to be competitive in the 2024 presidential election. Given Trump's historical performance in previous campaigns, particularly the 2016 election, it is more insightful to model his election outcomes. To achieve this, we have decided to create a Bayesian Hierarchical Model.

@@

# Results {#sec-result}

@@

# Discussion {sec-discussion}

@@

# Appendix 1 {#sec-appendix-one}

@@

# Appendix 2 : Idealized Survey {#sec-appendix-two}

@@

# Appendix 3 : Model Details {#sec-appendix-three}

@@

# References {#sec-reference}
